---
title: "Alcohol vs Seat choice"
author: "Daniella Parra"
date: "Summer 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

As shown in the boxplot, the back row is higher up, than the front and middle. 
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

In this boxplot, we can tell the difference of the box of the backrow is slightly bigger than the first boxplot we saw above.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The back row is drasticly different with their mean being 9.6. The middle row being 3.2. The front row holding the lowest at 1.8. 


## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

We will reject this hypothesis, but we will seek clarification on which rows were different from other rows. 

```{r}
plot(TukeyHSD(model1))
```

Using the Tukey plotbox we can tell that the front is different from the back, and the middle is different from the back. However there is no difference between the middle and the front. 

## Conclusions


